---
title: "@ alberta"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: flatly
---

### Alberta Overview

```{r}
library("leaflet")

m <- leaflet()
m <- addTiles(m)
m <- addMarkers(m, lng=-113.4909, lat=53.5444, popup="Edmonton - Capital of Alberta")
m <- addMarkers(m, lng=-114.0618, lat=51.0480, popup="Calgary - Largest City of Alberta")

m <- setView(m, lng=-113.4909, lat=53.5444, zoom = 9)

m
```

*** 

Alberta (/æl'b????rt??/) is a western province of Canada. With an estimated population of 4,196,457 as of July 1, 2015,[1][5] it is Canada's fourth-most populous province and the most populous of Canada's three prairie provinces. Its area is about 660,000 square kilometres (250,000 sq mi). Alberta and its neighbour Saskatchewan were districts of the Northwest Territories until they were established as provinces on September 1, 1905.[6] The premier has been Rachel Notley since May 2015.

### Frame 2

```{r}
```

*** 

Some commentary about Frame 1.

### Frame 3

```{r}
```

*** 

Some commentary about Frame 1.

### Frame 4

```{r}
```

*** 

Some commentary about Frame 1.

### Frame 5

```{r}
```

*** 

Some commentary about Frame 1.

### Frame 6

```{r}
```

*** 

Some commentary about Frame 1.
